SMT-Boosted Security Types for Low-Level MPC

### 2024-10-11 esop25/cpj.tex
checkpoint

The syntax of types $\ty$ and type environments $\Gamma$ are presented
in Figure \ref{fig-cpj}. We also
define type judgements for expressions and programs by direct
interpretation as terms $\phi$ and constraints $\eqs$ respectively,
via the encoding $\toeq{\cdot}$. The \TirName{Encode} rule captures
the use ``fresh'' samples for encryption discussed above. Derivations
enforce linearity by requiring that variables used for encryption
are added to judgements, and guaranteed to not be used elsewhere
via a form of union that ensures disjointness of combined sets:
\begin{definition}
  $R_1;R_2 = R_1 \cup R_2$ if $R_1 \cap R_2 = \varnothing$ and is otherwise
  undefined.
\end{definition}
The \TirName{DepTy} rule handles all other syntactic forms and just
records the dependencies on variables in the term.  The \TirName{Send}
rule records the types of messages, reveals, and outputs in
enviroments, and the \TirName{Seq} rule combines the types of
sequenced programs.  Given this we define validity of program type
judgements as follows. 
\begin{definition}
  Given preprocessing predicate $\eqspre$ and protocol $\prog$ we say
  $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$ is \emph{valid} iff it is derivable and
  $\eqspre \wedge \toeq{\prog} \models \eqs$.
\end{definition}
It is important to note that this presentation of derivations is
logical, not algorithmic-- in particular it is not syntax-directed
due to the \TirName{Encode} rule.

@@

\begin{definition}
  Given $\prog$ with $\iov(\prog) = S \cup V \cup O$, we say that
  $X \subseteq S \cup \flips(\prog)$ \emph{interfere with} 
  $M \subseteq V$ iff $\progd{\prog} \not\vdash X * M$.
\end{definition}

>>>>

The syntax of types $\ty$ and type environments $\Gamma$ are presented
in Figure \ref{fig-cpj}\footnote{In general we use $2^{\chi}$ to denote
the powerset of terms in any grammatical sort $\chi$.}. We also
define type judgements for expressions and programs by direct
interpretation as terms $\phi$ and constraints $\eqs$ respectively,
via the encoding $\toeq{\cdot}$. The \TirName{Encode} rule captures
the use ``fresh'' samples for encryption discussed above. Derivations
enforce linearity by requiring that variables used for encryption
are added to judgements, and guaranteed to not be used elsewhere
via a form of union that ensures disjointness of combined sets:
\begin{definition}
  $R_1;R_2 = R_1 \cup R_2$ if $R_1 \cap R_2 = \varnothing$ and is otherwise
  undefined.
\end{definition}
The \TirName{DepTy} rule handles all other syntactic forms and just
records the dependencies on variables in the term.  The \TirName{Send}
rule records the types of messages, reveals, and outputs in
enviroments, and the \TirName{Seq} rule combines the types of
sequenced programs.  Given this we define validity of program type
judgements as follows. 
\begin{definition}
  Given preprocessing predicate $\eqspre$ and protocol $\prog$ we say
  $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$ is \emph{valid} iff it is derivable and
  $\eqspre \wedge \toeq{\prog} \models \eqs$.
\end{definition}
It is important to note that this presentation of derivations is
logical, not algorithmic-- in particular it is not syntax-directed
due to the \TirName{Encode} rule.

@@

\begin{definition}
  Given $\prog$ with $\iov(\prog) = S \cup V \cup O$, we say that
  $X \subseteq S \cup \flips(\prog)$ \emph{interfere with} 
  $M \subseteq V$ iff $\progd(\prog) \not\vdash X * M$.
\end{definition}

### 2024-10-11 esop25/ipj.tex
checkpoint

\begin{definition}
  Given $H,C$ and $\prog$ with $\views(\prog) = V$ and $\secrets(\prog) = S$,
  $\adversary$, and $\store \in \aruns(\prog)$, we say $\store$ is
  \emph{aberrant through $V' \subseteq V$} if $\neg\exists \store' \in \runs(\prog) .
  \store_{S_H \cup V'} = \store'_{S_H \cup V'}$, and if there exists
  such $\adversary$ and $\store$ we say any
  $x \in V'$ is \emph{in an aberration}.
\end{definition}

\begin{lemma}
  If $\prog$ does not have integrity for some $H,C$, then it has
  aberrant $\store \in \aruns(\prog)$ for some $\adversary$. 
\end{lemma}

\begin{lemma}
  Given $\prog$ and $H,C$, if $x$ is in an aberration then one of
  the two inductively defined conditions holds:
  \begin{enumerate}[\hspace{5mm}i.]
  \item There exists $\xassign{x}{\be}{\cid} \in \prog$ with $\cid \in C$.
  \item There exists $\xassign{x}{\be}{\cid} \in \prog$ with $\cid \in H$ and
    $x' \in \vars(\be)$ such that $x'$ is in an aberration.
  \end{enumerate}
\end{lemma}

\begin{lemma}
  Given pre-processing predicate $\eqspre$ and protocol $\prog$ with
  $\views(\prog) = V$, if 
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  and $x\in V$ has an aberration for some $H,C$,
  then $\cheatj{\Delta}{H,C}{\seclev}$ and $\seclev(x) = \lolab$.
\end{lemma}

>>>>

\begin{definition}
  Given $H,C$ and $\prog$ with $\secrets(\prog) = S$ and $x \in \views(\prog)$,
  we say $x$ has an \emph{aberration} iff
  $\exists \adversary, \store \in \botruns(\prog)$ such that $\store(x) \ne \bot$
  and $\neg\exists \store' \in \runs(\prog) .
  \store_{S_H \cup \setit{x}} = \store'_{S_H \cup \setit{x}}$.
\end{definition}

\begin{lemma}
  If $\prog$ with $\views(\prog) = V$ does not have integrity for some
  $H,C$, then there exists $x \in \houtputs$ with an
  aberration.
\end{lemma}

\begin{lemma}
  Given $\prog$ and $H,C$, if $x$ has an aberration then one of
  the two inductively defined conditions holds:
  \begin{enumerate}[\hspace{5mm}i.]
  \item There exists $\xassign{x}{\be}{\cid} \in \prog$ with $\cid \in C$.
  \item There exists $\xassign{x}{\be}{\cid} \in \prog$ with $\cid \in H$ and
    $x' \in \vars(\be)$ such that $x'$ has an aberration.
  \end{enumerate}
\end{lemma}

\begin{lemma}
  Given pre-processing predicate $\eqspre$ and protocol $\prog$ with
  $\views(\prog) = V$, if 
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  and $x$ has an aberration for some $H,C$,
  then $\cheatj{\Delta}{H,C}{\seclev}$ and $\seclev(x) = \lolab$.
\end{lemma}
